Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-08 fib2.tex
start to explain topological ops

>>>>

\section{Computation of logical operators}

Here we show a process where a 
tau anyon is wrapped around the torus twice.
The vertical lines represent a periodic
identification, and we leave anyons paths
as undirected because Fibonacci anyons are
self-inverse.
The dotted lines represent vacuum charges,
and we are free to include these lines or
not.
\begin{align*}
\includegraphics[]{pic-logops.pdf}
\end{align*}

The state is not normalized.
Also involves post-selection, as there is
another process that involves leakage...
The first equation is an $F$-move, 
the second equation is a translation in the
horizontal direction, and the last equation
follows from the rule for collapsing bubbles.

Continuing in this way, we compute the $k$-fold
logical operator:
\begin{align*}
\includegraphics[]{pic-kfold.pdf}
\end{align*}

where $f_k$ is the $k$-th element of the Fibonacci
sequence $\{1, 1, 2, 3...\}.$
